\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}
\geometry{margin=0.6in}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.4ex}
\usepackage{enumitem}
\usepackage{titlesec}

\titleformat{\section}[block]{\large\bfseries}{}{0pt}{}[\titlerule]

\begin{document}

\begin{center}
    {\LARGE \textbf{K S Sumukha Vasista}} \\
    \vspace{0.1cm}
    \href{mailto:sumukhavst@gmail.com}{sumukhavst@gmail.com} | +91 8088510860 | \href{https://github.com/sumukhavasista}{GitHub URL}
\end{center}

\vspace{0.2cm}

\section*{SUMMARY}
Aspiring Computer Science Engineer currently pursuing a Bachelor's degree in Engineering from Jyothy Institute of Technology affiliated to VTU. Passionate about coding, problem-solving, Cybersecurity, and GenAI. Seeking to leverage academic knowledge and practical skills in a dynamic and challenging environment.

\section*{EDUCATION}
\begin{itemize}[leftmargin=0.3cm, itemsep=0pt, topsep=0pt]
    \item \textbf{Schooling / 10th} \\
    Percentage – 70\% \\
    SSM Public School, Bengaluru \\
    Graduation Date: October 2019

    \item \textbf{B.E in Computer Science Engineering} \\
    Current CGPA – 7 \\
    Visvesvaraya Technological University (VTU), India \\
    Expected Graduation: 2025
\end{itemize}

\section*{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=0.3cm, itemsep=0pt, topsep=0pt]
    \item \textbf{Programming Languages:} HTML, CSS, JavaScript Basics, C
    \item \textbf{Design Tools:} Adobe Photoshop, Adobe After Effects
    \item \textbf{Operating Systems:} Windows, Linux, Kali Linux
\end{itemize}

\section*{ACADEMIC PROJECTS}
\begin{itemize}[leftmargin=0.3cm, itemsep=0pt, topsep=0pt]
    \item \textbf{A simple hotel room booking platform/website} (2024) \\
    Led a team of 2; Created a single website which contains the details of all the hotels present in the particular city. \\
    \textit{Frontend:} HTML, CSS, JavaScript; \textit{Backend:} MySQL, Node.js \\
    The website is currently 90\% accurate, but still it works without any error at any end of the website.

    \item \textbf{Image Compression using Python (OpenCV)} (2023) \\
    Created a simple application for compressing color images using OpenCV library. \\
    This app helps to compress any type of images with a value of 1-100. \\
    \href{https://github.com/sumukhavasista/image_compression}{GitHub link of project}

    \item \textbf{Personal Portfolio} (Currently Working) \\
    Using React, I am currently working on creating my own portfolio which shows my personal information in the form of a website. \\
    \href{https://github.com/sumukhavasista/my-portfolio}{GitHub link of the project}

    \item \textbf{Performed an attack on Windows 11 (Internship provided by college)} (2022) \\
    With basic knowledge of Network Security, VAPT, Nmap, Wireshark, Nessus, we worked on performing an attack on Windows 11. \\
    This project was about hacking Windows 11 and gaining control of the other end system, successfully created with the help of Enterprise Building Solutions (EBTS) and Jyothy Institute of Technology.
\end{itemize}

\section*{OTHER ACTIVITIES/INTERESTS}
Passionate about learning and exploring Generative AI and Cybersecurity, with a keen interest in developing innovative projects in these fields. Eager to apply theoretical knowledge and practical skills to create impactful AI-driven solutions and enhance digital security measures.

\section*{CERTIFICATIONS}
\begin{itemize}[leftmargin=0.3cm, itemsep=0pt, topsep=0pt]
    \item \textbf{Web Development with Python and Django} \\
    \href{https://www.udemy.com/certificate/UC-22045d1d-ebe3-4771-855e-86a40fee6b02/}{View Certificate}
\end{itemize}

\end{document}
